\Large \bf Security Audit of Safeplug ``Tor in a Box''

### 2014-07-11 foci/paper.tex
updated performance measurement section and future work section, added citations

\title{\Large \bf Security Audit of Safeplug ``Tor in a Box''}
%\author{
% {\rm Anne Edmundson}\\
% Princeton University
% \and
% {\rm Anna Kornfeld Simpson}\\
% Princeton University
% \and
% {\rm Joshua Kroll}\\
% Princeton University
% \and
% {\rm Edward Felten}\\
% Princeton University
%} % end author

@@

Table \ref{versions} shows the software used by the device, the corresponding version of the software, the date of that version's release, and if it is up to date as of May 2014.  There are many known vulnerabilities in the pieces of software that are not up to date.

@@

For each of the settings, we took 20 measurements [TODO: explain why only 20 measurements]; Figure~\ref{fig:latency2} shows the average time of a web request on each of the specified settings for three different web pages.  When taking these measurements, we loaded the page, but did not scroll; in many cases more objects are loaded when scrolling down a page.  The differences between web pages can most likely be attributed to the amount of advertisements and content running in plugins (such as video) on the web page.

@@

TODO: talk about variation within specific categories for each site.

@@

TODO: mention caveat that we might just be seeing variation in circuit performance because close timing of fetches.

@@

\section{Future Work}
TODO: Talk about performance measurements - specifically to do more than 20 fetches and spread the fetches out over time to ensure different Tor circuits.  Talk about privoxy vs tbb measurements - improvements.

>>>>

\title{\Large \bf Security Audit of Safeplug ``Tor in a Box''}
\author{
 {\rm Anne Edmundson}\\
 Princeton University
 \and
 {\rm Anna Kornfeld Simpson}\\
 Princeton University
 \and
 {\rm Joshua Kroll}\\
 Princeton University
 \and
 {\rm Edward Felten}\\
 Princeton University
} % end author

@@

Table \ref{versions} shows the software used by the device, the corresponding version of the software, the date of that version's release, and if it is up to date as of May 2014.  There are many known vulnerabilities in the pieces of software that are not up to date~\cite{cve1, cve2, cve3}.

@@

For each of the settings, we took 20 measurements because we were confident this would give us enough data points that would span multiple Tor circuits; Figure~\ref{fig:latency2} shows the average time of a web request on each of the specified settings for three different web pages.  When taking these measurements, we loaded the page, but did not scroll; in many cases more objects are loaded when scrolling down a page.  The differences between web pages can most likely be attributed to the amount of advertisements and content running in plugins (such as video) on the web page.

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.5\textwidth]{rangeanddistcocacola}
  \caption{Web request time variation for www.coca-cola.com.}
  \label{fig:boxandwhisker}
\end{figure*}

Figure~\ref{fig:boxandwhisker} displays the variation among fetch requests for each setting when fetching \url{www.coca-cola.com}.  The greater variation for settings using Tor leads us to believe that more than one Tor circuit was used.  Despite performing these fetches close in time, this variation shows that more than one Tor circuit was used, and therefore, we were not simply measuring the variation in Tor circuit performance.

@@

@@

\section{Future Work}
A more in-depth analysis of the performance of the Safeplug would be useful in the future.  The performance of the Safeplug reflects it's usability, and would be helpful in determining the trade-offs of using the device.  Additionally, a greater breadth of privacy measurements would cement Safeplug's position as a useful privacy-preserving technology, or a device that doesn't protect privacy as well as other tools.
